Brief Announcement: An Improved Lower Bound for Dynamic Balanced Graph Partitioning

### 2020-02-17 paper/paper.tex
Intro

Main technical contribution of this paper is the lower bound $\Omega(k\cdot\ell)$ for the competitive ratio of any deterministic algorithm for Online Balanced Partition problem (cf. Section~\ref{sec:lowerbound}).
The best known lower bound so far was $\Omega(k)$ \cite{repartition-disc}
which involves only two cluster.

So far, the competitive ratio of the best known algorithm was the component-based algorithm with the ratio $O(k^2\cdot \ell^2)$ \cite{repartition-disc}.
We present an optimal algorithm for $k=3$ in Section~\ref{sec:k3}.
In Section~\ref{sec:ppl}, we present a $O(k\cdot \ell)$-competitive algorithm for the restricted scenario
where the communication graph (i.e., request sequence) admits a \emph{perfect partition} (i.e., a multi-way cut of cost zero) that is also an optimal configuration for the offline problem.
For this setting, the algorithm is optimal, as the lower bound utilized an input sequence that has a perfect partition.

>>>>

Main technical contribution of this paper is the lower bound $\Omega(k\cdot\ell)$ (Section~\ref{sec:lowerbound}) for the competitive ratio of any deterministic algorithm for online Balanced RePartition problem..
The best known lower bound so far was $\Omega(k)$ \cite{repartition-disc}
which involves only two cluster.

So far, the competitive ratio of the best known algorithm was the component-based algorithm with the ratio $O(k^2\cdot \ell^2)$ \cite{repartition-disc}.
By applying classic rent-or-buy technique, we obtained an optimal algorithm for $k=3$, that we present in Section~\ref{sec:k3}.

In Section~\ref{sec:ppl}, we study a restricted model of Balanced RePartition, called Perfect Partition.
For that, we present a $O(k\cdot \ell)$-competitive algorithm that is optimal.
We believe that this result is an important building block on the way to an optimal algorithm for the general model.
